Comparing the Enriched Hits of Different Probes

### 2025-10-31 Background/DataAnalysisAndStatistics.qmd
Fixed reference links

* This embedded Shiny app allows the user to select two datasets to visually compare along the axes of a scatter plot.
* **Crucially, this tool is not intended for quantitative comparisons, as described in greater detail above in [@sec-DataAlignment].**
* The statistical annotations of each dataset are compared and distinguished along the axes and denoted by color: 
  * Black proteins are unenriched in respect to both probes.
  * Purple proteins are “enriched” with respect to only the probe on the x-axis.
  * Green proteins are “enriched” with respect to only the probe on the y-axis.
  * Orange proteins are “enriched” in both probes.

>>>>

* This embedded Shiny app allows the user to select two datasets to visually compare along the axes of a scatter plot.
* **Crucially, this tool is not intended for quantitative comparisons, as described in greater detail above in [Data Alignment @sec-DataAlignment].**
* The statistical annotations of each dataset are compared and distinguished along the axes and denoted by color: 
  * Black proteins are unenriched in respect to both probes.
  * Purple proteins are “enriched” with respect to only the probe on the x-axis.
  * Green proteins are “enriched” with respect to only the probe on the y-axis.
  * Orange proteins are “enriched” in both probes.

### 2025-10-31 ProbeVsProbeComparison/EnrichedHitsComparison.qmd
Updating with reviewer changes and some reorganization
Fixed broken links and section references caused by reorg
Fixed reference links

@@

This Shiny app plots the enrichment results of two user-selected datasets against each other for visual comparison of protein enrichment toward each lipid probe. Use the dropdown menus to select lipid probes to plot against each other and visualize the enriched hits of each probe. Proteins missing in one dataset are temporarily assigned a logFC of 0 for visualization -- thus, they will appear along one axis. Black proteins are unenriched in respect to both probes; Purple proteins are "enriched" with respect to only the probe on the x-axis; Green proteins are "enriched" with respect to only the probe on the y-axis; and Orange proteins are "enriched" in both probes. The red dashed line denotes the line of best fit between the datasets, determined via linear regression (the red text denotes the line formula and adjusted R^2^ value). Note that the significance thresholds for each dataset are as defined on the respective lipid probe or studies page and are not the same between studies -- this page is intended for a simple qualitative comparison of hits between datasets.

>>>>

See our [Data Analysis & Statistics](https://lipidinteractome.org/background/dataanalysisandstatistics#sec-DataAlignment) background page for greater detail on the data alignment performed to enable this qualitative comparison.

@@

This Shiny app plots the enrichment results of two user-selected datasets against each other for visual comparison of protein enrichment toward each lipid probe. Use the dropdown menus to select lipid probes to plot against each other and visualize the enriched hits of each probe. Proteins missing in one dataset are temporarily assigned a logFC of 0 for visualization -- thus, they will appear along one axis. Black proteins are unenriched in respect to both probes; Purple proteins are "enriched" with respect to only the probe on the x-axis; Green proteins are "enriched" with respect to only the probe on the y-axis; and Orange proteins are "enriched" in both probes. The red dashed line denotes the line of best fit between the datasets, determined via linear regression (the red text denotes the line formula and adjusted R^2^ value). **Note that the significance thresholds for each dataset are as defined on the respective lipid probe or studies page and are not the same between studies -- this page is intended for a simple qualitative comparison of hits between datasets. See [here](https://lipidinteractome.org/background/dataanalysisandstatistics#sec-ProbevsProbeComparisonBackground) for more detail.**
